\ifdefined\MAINTEXT \else Supplemental Material: \\ \fi Low-cost linear-scaling \emph{ab initio} molecular dynamics for weakly-interacting systems

### 2017-10-03 almo-langevin.tex

\author{Hayden Scheiber}
% RZK update email
\email{hayden.scheiber@mcgill.ca}
\author{Yifei Shi}
\author{Rustam Z. Khaliullin}
\email{rustam.khaliullin@mcgill.ca}
\affiliation{Department of Chemistry, McGill University, 801 Sherbrooke St. West, Montreal, QC H3A 0B8, Canada}

@@

\begin{figure}
\includegraphics[trim={0.5cm 0cm 0.7cm 0.1cm},clip,width=8.6cm]{DeltaForceComparison_with_ACF.eps}
\caption{\label{fig:randomforce}  
%RZK: Change panels: Remove panel (a), old panel (c) becomes new panel (a), old (b) -> new (b), old (d) -> new (c). The caption and the text has aready been re-written. 
The red line is the Euclidean norm of the instantaneous error $\langle \| \delta \vec{f_{i}}(t) \| \rangle_{i}$, the black line is the magnitude of the time average of the instantaneous error vector, and the green line is the time average of the red line. 
%(a) $R_{c} = 1.6$ vdWR and $\epsilon_{\text{SCF}} = 10^{-2}$~a.u. relative to the fully converged ALMO reference, 
(a) $R_{c} = 1.6$ vdWR and $\epsilon_{\text{SCF}} = 10^{-2}$~a.u., 
(b) $R_{c} = 1.6$ vdWR and fully converged ALMO SCF, 
(c) Normalized ACF of the instantaneous error in panel (a) $\frac{1}{3}\langle \delta \vec{f}_i (t) \cdot \delta\vec{f}_i(t+\tau) \rangle_{it} $.
%Forces are computed with the PBE XC functional and TZV2P basis set for the configurations from a 10-ps trajectory generated with KS-based AIMD at T=298~K. 
}
\end{figure}

@@

\begin{figure}
\includegraphics[trim={2.5cm 0.5cm 3.4cm 0.1cm},clip,width=8.6cm]{strongscaling_log.eps}
\caption{\label{fig:strongscaling_log} Timing benchmarks for PBE/TZV2P simulations of liquid water on 256 compute cores. 
%Logscale plots which show the asymptotic LS behaviour of ALMO methods for liquid water at 298 K.
%Compared with the orbital transformation using fully converged SCF and second generation Car-Parinello force calculation methods.~\cite{a:ot,a:ot2,a:2ndcpmd}
For ALMO methods, $R_{c} = 1.6$ vdWR. 
Cyan lines represent perfect cubic scaling, whereas gray lines represent perfect linear scaling. 
%RZK: On figure remove 'DFT', 'Wall-clock time' -> 'Wall time'. Decrease the height of the figure (the y-axis label is now shorter).
}
\end{figure}

@@

\begin{figure}
\includegraphics[trim={1.6cm 0cm 4.7cm 0cm},clip,width=8.6cm]{weakscaling.eps}
\caption{\label{fig:weakscaling} Weak scalability benchmarks for PBE/TZV2P ALMO AIMD with  $R_{c} = 1.6$ vdWR and $\epsilon_{\text{SCF}} = 10^{-2}$~a.u. 
Dashed gray lines connect systems simulated on the same number of cores to confirm LS behavior. %over a range of configurations.
%RZK: On figure 'Wall-clock time' -> 'Wall time', legend - increase font size, decrease the height of the figure(the y-axis label is now shorter). Replace cross symbols on magenta line with another "solid" symbol such as diamon or inverse triangle.
}
\end{figure}

>>>>

\author{Hayden Scheiber}
% RZK update email
\email{scheiber@chem.ubc.ca}
\author{Yifei Shi}
\author{Rustam Z. Khaliullin}
\email{rustam.khaliullin@mcgill.ca}
\affiliation{Department of Chemistry, McGill University, 801 Sherbrooke St. West, Montreal, QC H3A 0B8, Canada}

@@

\begin{figure}
\includegraphics[trim={0.5cm 0cm 0.7cm 0.1cm},clip,width=8.6cm]{DeltaForceComparison_with_ACF.eps}
\caption{\label{fig:randomforce}  
The red line is the Euclidean norm of the instantaneous error $\langle \| \delta \vec{f_{i}}(t) \| \rangle_{i}$, the black line is the magnitude of the time average of the instantaneous error vector, and the green line is the time average of the red line. 
%(a) $R_{c} = 1.6$ vdWR and $\epsilon_{\text{SCF}} = 10^{-2}$~a.u. relative to the fully converged ALMO reference, 
(a) $R_{c} = 1.6$ vdWR and $\epsilon_{\text{SCF}} = 10^{-2}$~a.u., 
(b) $R_{c} = 1.6$ vdWR and fully converged ALMO SCF, 
(c) Normalized ACF of the instantaneous error in panel (a) $\frac{1}{3}\langle \delta \vec{f}_i (t) \cdot \delta\vec{f}_i(t+\tau) \rangle_{it} $.
%Forces are computed with the PBE XC functional and TZV2P basis set for the configurations from a 10-ps trajectory generated with KS-based AIMD at T=298~K. 
}
\end{figure}

@@

\begin{figure}
\includegraphics[trim={2.5cm 0.5cm 3.4cm 0.9cm},clip,width=8.6cm]{strongscaling_log.eps}
\caption{\label{fig:strongscaling_log} Timing benchmarks for PBE/TZV2P simulations of liquid water on 256 compute cores. 
%Logscale plots which show the asymptotic LS behaviour of ALMO methods for liquid water at 298 K.
%Compared with the orbital transformation using fully converged SCF and second generation Car-Parinello force calculation methods.~\cite{a:ot,a:ot2,a:2ndcpmd}
For ALMO methods, $R_{c} = 1.6$ vdWR. 
Cyan lines represent perfect cubic scaling, whereas gray lines represent perfect linear scaling. 
}
\end{figure}

@@

\begin{figure}
\includegraphics[trim={1.6cm 0.8cm 4.7cm 0cm},clip,width=8.6cm]{weakscaling.eps}
\caption{\label{fig:weakscaling} Weak scalability benchmarks for PBE/TZV2P ALMO AIMD with  $R_{c} = 1.6$ vdWR and $\epsilon_{\text{SCF}} = 10^{-2}$~a.u. 
Dashed gray lines connect systems simulated on the same number of cores to confirm LS behavior. %over a range of configurations.
}
\end{figure}
